Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-10-02 paper.tex
Add captions for new figures

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\linewidth]{img/fig-emt-uncertainty.pdf}
  \caption{\label{fig-emt} \textbf{Failure of the effective 2D
      ``dielectric constant'' picture based on the effective medium
      theory (EMT)}. \textbf{a}.  Scheme of the EMT picture where an
    effective 2D ``dielectric constant'' $\varepsilon_{\mathrm{2D}}$
    is extracted from $\varepsilon_{\mathrm{SL}}$, which depends on
    the thickness $\delta_{\mathrm{2D}}$ of the 2D material that is
    not well-defined. \textbf{b}.  Estimation error between
    $\delta_{\mathrm{2D}}^{\parallel, \text{fit}}$ and
    $\delta_{\mathrm{2D}}^{\perp, \text{fit}}$ from non-linear fitting
    of /ab initio/ $\varepsilon_{\mathrm{SL}} - L$ data for selected
    2D metal dichacolgenides. The uncertainty of
    $\delta_{\mathrm{2D}}$ causes considerable variation of estimated
    $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{c}.) and in
    particular $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{d}.).  }
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D materials}. \textbf{a}. The structures of
  the 2D materials investigated in this
  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
  (blue dots) for all the 2D materials studied.
  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. HSE06 functional is used to obtain the data. \textbf{c}.
  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the background. \textbf{d}.
  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
  in the inset), showing a perfect linear relation with slope very
  close to $1/4\pi$ (i.e.
  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
  revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
  and Ref.~\cite{Mounet_2018} (triangles) as superimposed on
  \textbf{c} and \textbf{d}.}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.9\linewidth]{img/fig4.pdf}
\caption{\label{fig-4} \textbf{Application of 2D polarizability to
    multilayer and 3D systems}.  \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart.  By applying the concept of
  electronic polarizability to multilayer 2D materials, the multilayer
  polarizabilities $\alpha_{\mathrm{NL}}^{\parallel}$ and
  $\alpha_{\mathrm{NL}}^{\perp}$ of selected 2D metal dichacolgenides
  as functions of number of layers $N$ are shown in \textbf{a} and
  \textbf{b}, respectively. Both $\alpha_{\mathrm{NL}}^{\parallel}$
  and $\alpha_{\mathrm{NL}}^{\perp}$ linearly scales with $N$ and the
  electronic polarizabilities of monolayer, indicating that
  $\alpha_{\mathrm{2D}}$ is an additive quantity under weak
  interacting regime. The 2D to 3D transition is further studied in
  \textbf{c} and \textbf{d}, where $\alpha_{\mathrm{2D}}$ of an
  monolayer 2D material is compared with its bulk counterpart
  $\varepsilon_{\mathrm{Bulk}}$. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good
  correlation. \textbf{d} $\varepsilon_{\mathrm{bulk}}^{\perp}$
  calculated from DFT (y-axis) compared with the predicted value from
  2D $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis). The predicted value
  is in good aggreement with the DFT calculation when
  $E_{\mathrm{g}}>4$ eV, due to minimal interlayer coupling. The
  comparisons in \textbf{b} and \textbf{c} are made based on both
  HSE06 (circles) and PBE (squares) functionals.}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width-0.8\linewdith]{img/fig-ellipsoid.pdf}
  \caption{\label{fig-ellip} \textbf{Geometric representation of the
      2D polarizability}. \textbf{a}. Scheme of the polarizability
    ellipsoid of a 2D material, with its in-plane
    ($r_{0}^{\parallel}$) and out-of-plane radii
    ($r_{\mathrm{0}}^{\perp}$) proportional to
    $\alpha_{\mathrm{2D}}^{\parallel}$ and
    $\alpha_{\mathrm{2D}}^{\perp}$, respectively.  The values of
    $r_{0}^{\parallel}$ and $r_{0}^{\perp}$ for selected 2D metal
    dichalcogenides are shown in \textbf{b} and \textbf{c},
    respectively.  }
\end{figure}

@@

\end{document}

>>>>

Add Mounet paper \cite{Mounet_2018}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\linewidth]{img/fig-emt-uncertainty.pdf}
  \caption{\label{fig-emt} \textbf{Failure of the effective 2D
      ``dielectric constant'' picture based on the effective medium
      theory (EMT)}. \textbf{a}.  Scheme of the EMT picture where an
    effective 2D ``dielectric constant'' $\varepsilon_{\mathrm{2D}}$
    is extracted from $\varepsilon_{\mathrm{SL}}$, which depends on
    the thickness $\delta_{\mathrm{2D}}$ of the 2D material that is
    not well-defined. \textbf{b}.  Estimation error between
    $\delta_{\mathrm{2D}}^{\parallel, \text{fit}}$ and
    $\delta_{\mathrm{2D}}^{\perp, \text{fit}}$ from non-linear fitting
    of \textit{ab initio} $\varepsilon_{\mathrm{SL}} - L$ data for selected
    2D TMDCs. The uncertainty of
    $\delta_{\mathrm{2D}}$ causes considerable variation of estimated
    $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{c}.) and in
    particular $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{d}.).  }
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D materials}. \textbf{a}. The structures of
  the 2D materials investigated in this
  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
  (blue dots) for all the 2D materials studied.
  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. HSE06 functional is used to obtain the data. \textbf{c}.
  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the background. \textbf{d}.
  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
  in the inset), showing a perfect linear relation with slope very
  close to $1/4\pi$ (i.e.
  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
  revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
  and Ref.~\citenum{Mounet_2018} (triangles) as superimposed on
  \textbf{c} and \textbf{d}.}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.9\linewidth]{img/fig4.pdf}
\caption{\label{fig-4} \textbf{Application of 2D polarizability to
    multilayer and bulk systems}.  \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart.  By applying the concept of
  electronic polarizability to multilayer 2D materials, the multilayer
  polarizabilities $\alpha_{\mathrm{NL}}^{\parallel}$ and
  $\alpha_{\mathrm{NL}}^{\perp}$ of selected 2D metal dichacolgenides
  as functions of number of layers $N$ are shown in \textbf{a} and
  \textbf{b}, respectively. Both $\alpha_{\mathrm{NL}}^{\parallel}$
  and $\alpha_{\mathrm{NL}}^{\perp}$ linearly scales with $N$ and the
  electronic polarizabilities of monolayer, indicating that
  $\alpha_{\mathrm{2D}}$ is an additive quantity under weak
  interacting regime. The 2D to 3D transition is further studied in
  \textbf{c} and \textbf{d}, where $\alpha_{\mathrm{2D}}$ of an
  monolayer 2D material is compared with its bulk counterpart
  $\varepsilon_{\mathrm{Bulk}}$. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis), showing good
  correlation. \textbf{d} $\varepsilon_{\mathrm{bulk}}^{\perp}$
  calculated from DFT (y-axis) compared with the predicted value from
  2D $\alpha_{\mathrm{2D}}^{\parallel}$ (x-axis). The predicted value
  is in good aggreement with the DFT calculation when
  $E_{\mathrm{g}}>4$ eV, due to minimal interlayer coupling. The
  comparisons in \textbf{b} and \textbf{c} are made based on both
  HSE06 (circles) and PBE (squares) functionals.}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\linewidth]{img/fig-ellipsoid.pdf}
  \caption{\label{fig-ellip} \textbf{Geometric representation of the
      2D polarizability}. \textbf{a}. Scheme of the polarizability
    ellipsoid of a 2D material, with its in-plane
    ($r_{0}^{\parallel}$) and out-of-plane radii
    ($r_{\mathrm{0}}^{\perp}$) proportional to
    $\alpha_{\mathrm{2D}}^{\parallel}$ and
    $\alpha_{\mathrm{2D}}^{\perp}$, respectively.  The values of
    $r_{0}^{\parallel}$ and $r_{0}^{\perp}$ for selected 2D TMDCs are
    shown in \textbf{b} and \textbf{c}, respectively.  The
    polarizability ellipsoid is highly anisotropic with screening much
    larger at in-plane direction than out-of-plane direction.}
\end{figure}

@@

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
